### 2016-09-27 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added abstract to burner report; acronyms to hose stream report

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
NF \> Narrow Fog Stream\\
NIST \> National Institute of Standards and Technology \\
SB \> Smooth Bore Stream\\
SS \> Straight Stream \\
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
WF \> Wide Fog Stream \\
\end{tabbing}

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
NF \> Narrow Fog Stream\\
NIST \> National Institute of Standards and Technology \\
OSB \> Oriented Strand Board \\
SB \> Smooth Bore Stream\\
SS \> Straight Stream \\
TJI \> Truss Joist I-beams \\ 
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
WF \> Wide Fog Stream \\
\end{tabbing}

### 2016-09-27 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added author names & abstract section heading to report
Added abstract to burner report; acronyms to hose stream report

\headerC{
{
\flushright{

@@

\headerC{
\flushright{

{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\vspace*{2\baselineskip}
May 2016}}

@@

\begin{tabbing}
\hspace{1.5in} \= \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests~2--6, were conducted in the East Structure. Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for Tests~2--4 and Tests~5--6, respectively. The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for one, two, and three burners, and for Tests~5 and 6, a single heat release rate for three burners is reported.
% Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

@@

\begin{table}[!ht]
\caption{Heat Release Rates for Tests~2--4}
\begin{tabular}{lccc}
 \toprule
 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} \textbf{One} \\ \textbf{Burner On} \end{tabular} 
					&	\begin{tabular}{c} \textbf{Two} \\ \textbf{Burners On} \end{tabular}
					&	\begin{tabular}{c} \textbf{Three} \\ \textbf{Burners On} \end{tabular} \\
 \midrule
Test 2 				& 560 & 1080 & 1470 \\
Test 3 				& 530 & 1040 & 1470 \\
Test 4				& 580 & 1140 & 1580 \\
\bottomrule
\end{tabular}
\label{table:HRR_Tests_2-4}
\end{table}

@@

>>>>

\headerC{
{
\flushright{
Joseph M. Willi \\
Craig G. Weinschenk \\
\vspace*{2\baselineskip}

@@

\headerC{
\flushright{
Joseph M. Willi \\
Craig G. Weinschenk$^*$ \\
{\em Fire Research Division \\
Engineering Laboratory} \\

@@

\vspace*{2\baselineskip}
September 2016}

\vspace*{2\baselineskip}
\textit{$^*$\small Currently with JENSEN HUGHES}
}

@@

\begin{tabbing}
\hspace{1.5in} \= \\
PPA \> Positive Pressure Attack \\
PPV \> Positive Pressure Ventilation \\ 
NIST \> National Institute of Standards and Technology \\
OSB \> Oriented Strand Board \\
TJI \> Truss Joist I-beams \\ 
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
\end{tabbing}

\chapter*{\centering Abstract}
\pagenumbering{gobble}
Nine full-scale fire experiments were conducted in two residential-scale structures to study how different fire fighting tactics, specifically horizontal, vertical, and positive pressure ventilation, affect the fire environment within a structure. The fire source for each experiment was provided by three propane burners. Five of the tests were conducted in a structure designed to simulate a single-story residential structure, and four of the tests were conducted in a structure designed to simulate a two-story residential structure. The structures were instrumented with sensors to collect local measurements of temperature, gas velocity, heat flux, and gas concentrations at various locations during the experiments. Different doors and vents were opened and closed during the tests to simulate horizontal and vertical ventilation. A PPV fan was also used during some of the experiments to further affect the ventilation conditions. This report contains detailed descriptions of the setup and procedure used for each of the nine experiments.

@@

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests, Tests~2--6, were conducted in the East Structure. Table~\ref{table:HRR_Tests_5-6} lists the heat release rates for Tests~5 and 6. The time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. As a result, a single heat release rate, one for all three burners ignited, is reported. The heat release rates for Tests~2--4 are not reported because they were not able to be accurately measured during the tests.
% The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds. Thus, for Tests~2--4, heat release rates are reported for one, two, and three burners, and for Tests~5 and 6, a single heat release rate for three burners is reported.
% Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.

@@

% \begin{table}[!ht]
% \caption{Heat Release Rates for Tests~2--4}
% \begin{tabular}{lccc}
%  \toprule
%  					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
% \textbf{Test} 		&	\begin{tabular}{c} \textbf{One} \\ \textbf{Burner On} \end{tabular} 
% 					&	\begin{tabular}{c} \textbf{Two} \\ \textbf{Burners On} \end{tabular}
% 					&	\begin{tabular}{c} \textbf{Three} \\ \textbf{Burners On} \end{tabular} \\
%  \midrule
% Test 2 				& 560 & 1080 & 1470 \\
% Test 3 				& 530 & 1040 & 1470 \\
% Test 4				& 580 & 1140 & 1580 \\
% \bottomrule
% \end{tabular}
% \label{table:HRR_Tests_2-4}
% \end{table}

@@

\chapter{Acknowledgments}
\label{chap:acknowledgments}
The authors would like to thank Daniel Madrzykowski (currently with UL FSRI), Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), and Keith Stakes (currently with UL FSRI) from NIST for their contributions in preparing and conducting these experiments. These experiments could not have been conducted without them.
